A Journey from Wild to Textbook Data to Reproducibly Refresh the Wages Data from the National Longitudinal Survey of Youth Database

### 2022-02-17 paper/paper.Rmd
updated according to reviewer comment

The `mean_hourly_wage` and `year` are set as the dependent and predictor, respectively. Furthermore, we use M-Estimation with Huber weighting, where the observation with a slight residual gets a weight of 1, while the larger the residual, the smaller the weight (less than 1) [@rlm]. <!--AE comment: “However, the challenging part of detecting the anomaly using the robustness weight is determining the weight threshold in which the observations are considered outliers.” I don’t think this sentence needs a “However” and probably should say “past which” rather than “in which”-->The challenging part of detecting the anomaly using the robustness weight is determining the weight threshold in which the observations are considered outliers. It should be noted that it is not possible to determine if all outliers are errors, and it might be that an individual had abnormally high wages at a particular time.

>>>>

The `mean_hourly_wage` and `year` are set as the dependent and predictor, respectively. Furthermore, we use iteratively reweighted least squares with Huber weighting, where the observation with a slight residual gets a weight of 1, while the larger the residual, the smaller the weight (less than 1) [@rlm]. <!--AE comment: “However, the challenging part of detecting the anomaly using the robustness weight is determining the weight threshold in which the observations are considered outliers.” I don’t think this sentence needs a “However” and probably should say “past which” rather than “in which”-->The challenging part of detecting the anomaly using the robustness weight is determining the weight threshold in which the observations are considered outliers. It should be noted that it is not possible to determine if all outliers are errors, and it might be that an individual had abnormally high wages at a particular time.
